Response to reviewers

### 2022-02-17 response/response1.Rmd
revised fig 2 according to reviewer comment"
update response

@@

@@

@@

>>>>

* The approach is for the case study only and is not meant to be extrapolated for other cases. We suggest using a robust mixed model as a better alternative, however, our attempt to fit such a model via `robustlmm` resulted in computational issues.

@@

* We have added in Introduction that "Section 3 presents the steps ... to find and repair anomalies.".

@@

* Thank you for your suggetion. We have modified the description to "To treat the extreme values in the data, we build a robust linear regression model where we use the robustness weight to determine if a value should be replaced with the fitted value from the model."

@@

* Thank you for your enquiry. We have re-written this section to better describe our process and intent. In particular, the threshold values are chosen based on extensive eye-balling of the plots of wages over time for each individual. We try to maintain a balance of not overly smoothing the observations but clearly repairing unlikely wage values. As alluded in the section, we believe that an alternative approach such as robust linear mixed models is more appropriate but we did not proceed with this as we had issues fitting the model with `robustlmm` package. In addition, we thought that the use of robust linear models is easier to explain in the context of teaching and the use of non-optimal approach can generate a good discussion about alternative approaches in class.
